### 2024-05-29 getting-started.qmd
20240528 - fix error and warning

```{r}
players$factorVar <- factor(players$ID)
players$numericVar <- as.numeric(players$age)
players$integerVar <- as.integer(players$newVar)
players$characterVar <- as.character(players$newVar1)
```

@@

#### Seasonal {#sec-calculateActualPointsWeekly}

#### Career {#sec-calculateActualPointsWeekly}

>>>>

```{r}
players$factorVar <- factor(players$ID)
players$numericVar <- as.numeric(players$age)
players$integerVar <- as.integer(players$newVar1)
players$characterVar <- as.character(players$newVar2)
```

@@

#### Seasonal {#sec-calculateActualPointsSeasonal}

#### Career {#sec-calculateActualPointsCareer}
